%Preamble
\documentclass{report} % The document class with options
\usepackage[T1]{fontenc} % Selectfont encoding
\usepackage{parskip}

%Document body
\begin{document}
Hello World!

This is my first document.

This is a simple
document\footnote{with a footnote}.

This is a new     paragraph ~~~~with several hard spaces.

Some text with \emph{emphasis and \emph{nested content}}.

Some text in \textit{italic and \textit{nested content}}.

Some text in \textbf{bold and \textbf{nested content}}.

\section{The Title of the First Section}

Text of materials in the first section.

The second paragraph of the first section.

\subsection{Subsection of the first section}

Text of materials in the subsection.

The second paragraph.

\subsubsection{Subsubsection of the subsection of the first section}

Text of materials in the subsubsection.

\paragraph{Paragraph in the subsubsection}

Text of materials in the paragraph.

The second paragraph.

\subparagraph{Subparagraph in the paragraph in the subsubsection}

Text of materials in the subparagraph.

The second paragraph.

\section{The Second Section}

Text of materials in the second section.

The second paragraph

Ordered\textunderscore1
\begin{enumerate}
  \item An entry
  \item Another One
  \item Wow! Three entries
\end{enumerate}

Unordered\textunderscore1
\begin{itemize}
  \item An entry
  \item Another One
  \item Wow! Three entries
\end{itemize}

\chapter{The Title of the First Chapter}
The creature lists.

\begin{description}
  \item[Animals] animals
    \begin{enumerate}
      \item Dog
      \item Cat
    \end{enumerate}
  \item[Plants] plants
    \begin{itemize}
      \item Grass
      \item Tree
        \begin{enumerate}
          \item Oak
          \item Pine
            \begin{itemize}
              \item Red Pine
                \begin{itemize}
                  \item Eastern White Pine
                    \begin{itemize}
                      \item First
                      \item Second
                      \item Third
                    \end{itemize}
                  \item Western White Pine
                \end{itemize}
              \item White Pine
            \end{itemize}
        \end{enumerate}
    \end{itemize}

\end{description}

\end{document}
